Google - Isolated Sign Language Recognition

### 2023-03-03 cvpr_final_report/PaperForReview.tex
Change wrong word

%------------------------------------------------------------------------
\section{Expected Result}
We hope creating the state-of-the-art model to predicted the American Sign Language (ASL) signs correctly
with the input data of every video frame landmarks captured by MediaPipe Holistic Solution.

>>>>

%------------------------------------------------------------------------
\section{Expected Result}
We hope creating the state-of-the-art model to predict the American Sign Language (ASL) signs correctly
with the input data of every video frame landmarks captured by MediaPipe Holistic Solution.
